---
layout: post
title:  StepOnePlus Uniformity Test
date:  2017-03-07 13:26:34
---

# Rationale
Testing the Baker Lab StepOnePlus machine for any potential variation among wells due to machine error/variability. Machine was calibrated (spatial, background, and dye) on 03/06/2017. To test for any variability, I will run a plate with 96 technical replicates, i.e., the same reaction in each well, that includes amplification of both C and D actin loci (VIC and FAM dyes, respectively.

# Methods
* Prepare DNA template: (210 µL total)
  + 10 µL Mc16-47t0 (Rivah's sample, contains clade C)
  + 10 µL 942-1 (see previous entry, contains clade D)
  + 180 µL H2O

* Prepare qPCR MasterMix:
  + Each reaction: 5 µL GTMM; 0.5 µL each of CFor, CRev, CProbe(VIC), DFor, DRev, DProbe(FAM); (no water)
  + MasterMix (n=98): 490 µL GTMM; 49 µL each oligo

* Add 8 µL MasterMix to each well
* Add 2 µL mixed C+D DNA template to each well

# Results

### Raw data files:  

[.eds]({{ site.baseurl }}/_source/2017-03-07-steponeplus-uniformity-test/20170307_RC_UniformityTest.eds)  
[.txt]({{ site.baseurl }}/_source/2017-03-07-steponeplus-uniformity-test/20170307_RC_UniformityTest_data.txt)

```{r import_data}
library(reshape2)
df <- read.delim("20170307_RC_UniformityTest_data.txt", skip=8)
df <- dcast(df, formula=Well~Target.Name, value.var="Cт")
```

### Visualize plates: 
```{r visualize_plates, fig.height=4, fig.width=6}
library(platetools)
raw_map(data=df$C, well=df$Well, plate=96)
raw_map(data=df$D, well=df$Well, plate=96)
```

### Run some stats:
```{r platestats}
library(effects)
library(lsmeans)

df$row <- factor(substr(df$Well, 1,1))
df$col <- factor(as.numeric(substr(df$Well, 2,3)))
df$corner <- factor(ifelse(df$Well %in% c("A1", "A12", "H1", "H12"), "corner", "not_corner"))
df$border <- factor(ifelse(df$row %in% c("A", "H") | df$col %in% c(1, 12), "border", "not_border"))
str(df)

# Are corners different?
mod <- lm(C ~ corner, data=df)
pairs(lsmeans(mod, specs="corner"))
plot(effect("corner", mod), main="Corner effect - C assay")

mod <- lm(D ~ corner, data=df)
pairs(lsmeans(mod, specs="corner"))
plot(effect("corner", mod), main="Corner effect - D assay")

# Are columns different? (excluding corners)
mod <- lm(C ~ col, data=subset(df, corner=="not_corner"))
anova(mod)
plot(effect("col", mod), main="Column effect - C assay (excluding corners)")

mod <- lm(D ~ col, data=subset(df, corner=="not_corner"))
anova(mod)
plot(effect("col", mod), main="Column effect - D assay (excluding corners)")

# Are rows different? (excluding corners)
mod <- lm(C ~ row, data=subset(df, corner=="not_corner"))
cld(lsmeans(mod, specs="row"))
plot(effect("row", mod), main="Row effect - C assay (excluding corners)")

mod <- lm(D ~ row, data=subset(df, corner=="not_corner"))
cld(lsmeans(mod, specs="row"))
plot(effect("row", mod), main="Row effect - D assay (excluding corners)")
```

### Conclusions:

Corners amplify ~1.3 cycles later than other wells.
Other wells in rows A and H (excluding corners!) amplify ~0.3 cycles later than other wells.
There is no effect of column.


