---
layout: post
title:  QuantStudio3 Uniformity Test
date:  2018-01-24 14:50:44
---


# Rationale
Testing the new QuantStudio3 machine for any potential variation among wells using a plate with 96 technical replicates, i.e., the same reaction in each well, that includes amplification of both C and D actin loci (VIC and FAM dyes, respectively).

# Methods
* Prepare DNA template: (200 µL total)
  + 100 µL clade C actin @ 64,000 copies/µL
  + 100 µL clade D actin @ 64,000 copies/µL

* Prepare qPCR MasterMix:
  + Each reaction: 5 µL GTMM; 0.5 µL each of CFor, CRev, CProbe(VIC), DFor, DRev, DProbe(FAM); (no water)
  + MasterMix (n=98): 490 µL GTMM; 49 µL each oligo

* Add 8 µL MasterMix to each well
* Add 2 µL mixed C+D DNA template to each well

# Results

### Raw data files:  

[.txt]({{ site.baseurl }}/_source/2018-01-24-quantstudio3-uniformity-test/2018-01-23_Uniformity-Test.txt)

```{r import_data}
library(reshape2)
df <- read.delim("2018-01-23_Uniformity-Test.txt", skip=7923, sep="\t")
df <- dcast(df, formula=Well.Position~Target.Name, value.var="CT")
```

### Visualize plates: 
```{r visualize_plates, fig.height=4, fig.width=6}
library(platetools)
raw_map(data=df$C, well=df$Well, plate=96)
raw_map(data=df$D, well=df$Well, plate=96)
```

### Run some stats:
```{r platestats}
library(effects)
library(lsmeans)

df$row <- factor(substr(df$Well, 1,1))
df$col <- factor(as.numeric(substr(df$Well, 2,3)))
df$corner <- factor(ifelse(df$Well %in% c("A1", "A12", "H1", "H12"), "corner", "not_corner"))
df$border <- factor(ifelse(df$row %in% c("A", "H") | df$col %in% c(1, 12), "border", "not_border"))
str(df)

# Are corners different?
mod <- lm(C ~ corner, data=df)
pairs(lsmeans(mod, specs="corner"))
plot(effect("corner", mod), main="Corner effect - C assay")

mod <- lm(D ~ corner, data=df)
pairs(lsmeans(mod, specs="corner"))
plot(effect("corner", mod), main="Corner effect - D assay")

# Are columns different? (excluding corners)
mod <- lm(C ~ col, data=subset(df, corner=="not_corner"))
anova(mod)
plot(effect("col", mod), main="Column effect - C assay (excluding corners)")

mod <- lm(D ~ col, data=subset(df, corner=="not_corner"))
anova(mod)
plot(effect("col", mod), main="Column effect - D assay (excluding corners)")

# Are rows different? (excluding corners)
mod <- lm(C ~ row, data=subset(df, corner=="not_corner"))
anova(mod)
cld(lsmeans(mod, specs="row"))
plot(effect("row", mod), main="Row effect - C assay (excluding corners)")

mod <- lm(D ~ row, data=subset(df, corner=="not_corner"))
anova(mod)
cld(lsmeans(mod, specs="row"))
plot(effect("row", mod), main="Row effect - D assay (excluding corners)")
```

### Conclusions:

Detection in the corners is 0.45 cycles later for C (VIC) and 0.2 cycles later for D (FAM). 

There is a significant column effect for D (FAM) detection.

There is a significant row effect for C (VIC) detection.

