---
layout: post
title:  Pooling samples for ezRAD libraries
date: 2016-05-27
---

I will pool individual samples from each of the three groups (Bleached clade C ("BC"), Not bleached clade C ("NC"), Not bleached clade D ("ND")) for ezRAD library preparation. 

Each group has 14 samples, and the library should have a total of 1300ng DNA going into the digest. Conservatively assuming 50% loss during a bead clean, I will create pools of 2600 ng DNA. Therefore, we need `r 2600/14` ng of each sample. Using the DNA concentrations from the AccuClear assay, the volumes of `r 2600/14` ng for each sample are: 

```{r}
samples <- read.csv("samples.csv")
dnaconc <- read.csv("dnaconc.csv")
data <- merge(samples, dnaconc, by="colony")
data$needvol <- (2600/14) / data$ng.uL
data <- with(data, data[order(group, sample.date, colony), ])
knitr::kable(data, row.names=F)
```
  
***  

###Total volume of pooled DNA for each group:

```{r}
groupvols <- with(data, aggregate(data.frame(vol_DNA=needvol), by=list(group=group), FUN=sum))
knitr::kable(groupvols)
```

PIPET ERROR: 8.8 µL of sample 20 (in "ND" pool) was added instead of 4.2 µL, so this sample will be overrepresented in the library.